\bf A Hierarchical Bayesian Approach for Modeling Infant-Mortality and Wearout Failure Modes

### 2017-06-23 paper/paper.tex
New outline

%\bibliographystyle{natbib}

@@

\newpage
\spacingset{1.45} % DON'T change the spacing!
\section{Introduction}
Failure distributions of high-reliability products, can be difficult
to assess. Accelerated testing tries to address this problem, but
requires strong assumptions to extrapolate to use conditions in the
field (citation). When field data are available, information may be
very limited. In this paper, we propose the use of Bayesian hierarchical modeling to borrow
information to improve inferences on lifetime
distributions where information is limited by right-censoring and
left-truncation.

@@

\subsection{Background}
In engineering applications, a product can often fail from one out of a set of possible malfunctioning components.  For example, a computer system can fail if the mother board, disc drive or power supply stop working.  Circuit boards (CB) can fail due to a manufacturing defect or later as a result of wearout.  The general name for such products is a series system where the lifetime of the product is the minimum failure time across $s$ different components or risks \cite{nelson}.  A common assumption in series systems is the time to failure for each risk, $s$, is statistically independent.  Thus, the overall reliability of a unit is modeled using the product rule across all $s$ risks.  Parameter estimation is straightforward if the cause of failure is known for each observation.  With engineering systems data, however, the exact cause of failure is frequently unknown or masked from the researcher.  \\

@@

\subsection{Motivation}
The goal of this paper is to model, and compare, the lifetime distribution of different hard drive brands using the GLFP lifetime model.  Product populations often contain a mixture of defective and non defective units.  The hazard function for this type of population is often described as a bathtub curve: the beginning of the curve corresponds to defective units failing early, followed by a constant hazard, and then and upswing as units fail from wearout.  Ignoring this hazard structure, which exists for series systems, could lead to spurious inference when comparing the reliability of hard drive-models \cite{sujata}.  The GLFP combines different failure time distributions to account for bending hazard functions; for example, one parametric model for defective units (infant mortality) and a second model for wearout \cite{chan}. \\

\section{Data}
Backblaze is a company that offers backup storage to protect against data loss.  While selling storage space is Backblaze's main business, since 2013 it has been collecting data on hard drives operating at its facility.  The purpose is to provide consumers and businesses with reliability information on different hard drive-models.  The hard drives continuously spin in controlled storage pods where they run until failure.  When a hard drive fails it is permanently removed, and new hard drives are regularly added to the storage pods.  In addition, the number of storage pods is increasing as Backblaze adds new drive-models to the sample.  Every quarter Backblaze makes its data publicly available through their website \cite{backblaze}. In addition, Backblaze publishes summary statistics of the different hard drive-models currently operating.  No other analysis or modeling of the failure data is provided; however, Backblaze does encourage the public to further analyze its data, which for this paper goes through the first quarter of 2016.

@@

@@

\section{Data analysis}

@@

\bibliographystyle{plainnat}
\bibliography{sample}

>>>>

\bibliographystyle{natbib}

@@

\newpage
\tableofcontents
\newpage
\spacingset{1.45} % DON'T change the spacing!
\section{Introduction}
You are a consumer with reliability data for products from multiple sources and wish to estimate lifetime, possibly for purposes of comparison.

We present a method for joint estimation of reliability data. This model is appropriate for products that have both early failures due to defect as well as due to wearout such as electronics. We illustrate this method in a setting where the information in the data is unevenly distributed across the populations of interest.

\subsection{Motivation}

Failure distributions of high-reliability products, can be difficult
to assess. Accelerated testing tries to address this problem, but
requires strong assumptions to extrapolate to use conditions in the
field (citation). When field data are available, information may be
very limited. In this paper, we propose the use of Bayesian hierarchical modeling to borrow
information to improve inferences on lifetime
distributions where information is limited by right-censoring and
left-truncation.

The goal of this paper is to model, and compare, the lifetime distribution of different hard drive brands using the GLFP lifetime model.  Product populations often contain a mixture of defective and non defective units.  The hazard function for this type of population is often described as a bathtub curve: the beginning of the curve corresponds to defective units failing early, followed by a constant hazard, and then and upswing as units fail from wearout.  Ignoring this hazard structure, which exists for series systems, could lead to spurious inference when comparing the reliability of hard drive-models \cite{sujata}.  The GLFP combines different failure time distributions to account for bending hazard functions; for example, one parametric model for defective units (infant mortality) and a second model for wearout \cite{chan}. \\

@@

\section{Background}
In engineering applications, a product can often fail from one out of a set of possible malfunctioning components.  For example, a computer system can fail if the mother board, disc drive or power supply stop working.  Circuit boards (CB) can fail due to a manufacturing defect or later as a result of wearout.  The general name for such products is a series system where the lifetime of the product is the minimum failure time across $s$ different components or risks \cite{nelson}.  A common assumption in series systems is the time to failure for each risk, $s$, is statistically independent.  Thus, the overall reliability of a unit is modeled using the product rule across all $s$ risks.  Parameter estimation is straightforward if the cause of failure is known for each observation.  With engineering systems data, however, the exact cause of failure is frequently unknown or masked from the researcher.  \\

@@

\section{GLFP model}
\subsection{Likelihood}
\subsubsection{With Truncation}
\subsection{Example 1}
Analysis of single drive model

@@

\section{Data analysis}
\subsection{Data}
Backblaze is a company that offers backup storage to protect against data loss.  While selling storage space is Backblaze's main business, since 2013 it has been collecting data on hard drives operating at its facility.  The purpose is to provide consumers and businesses with reliability information on different hard drive-models.  The hard drives continuously spin in controlled storage pods where they run until failure.  When a hard drive fails it is permanently removed, and new hard drives are regularly added to the storage pods.  In addition, the number of storage pods is increasing as Backblaze adds new drive-models to the sample.  Every quarter Backblaze makes its data publicly available through their website \cite{backblaze}. In addition, Backblaze publishes summary statistics of the different hard drive-models currently operating.  No other analysis or modeling of the failure data is provided; however, Backblaze does encourage the public to further analyze its data, which for this paper goes through the first quarter of 2016.

@@

@@

\bibliography{sample}
